\newcommand{\gSystemDiscounts}{{[}G1{]} The System has to encourage the user to have a good behaviour using discounts.}
\newcommand{\gSystemFees}{{[}G2{]} The System has to discourage the user to have a bad behaviour using fees.}
\newcommand{\gSystemDistribution}{{[}G3{]} The System has to ensure a good distribution of cars in the territory.}
\newcommand{\gSystemShare}{{[}G4{]} The System has to provide the ability to share a ride.}
\newcommand{\gVisitorSignUp}{{[}G5{]} The Visitor shall be able to sign-up via app.}
\newcommand{\gRegisteredLogin}{{[}G6{]} The Registered User shall be able to log into the service.}
\newcommand{\gRegisteredReserve}{{[}G7{]} The Registered User shall be able to reserve a car up to one hour before via app.}
\newcommand{\gRegisteredDeleteReservation}{{[}G8{]} The Registered User shall be able to remove a reservation before the reservation time runs out.}
\newcommand{\gRegisteredSearchDistance}{{[}G9{]} The Registered User shall be able to find the locations of available cars within a certain distance from him.}
\newcommand{\gRegisteredSearchAddress}{{[}G10{]} The Registered User shall be able to find the locations of available cars from a specified address.}
\newcommand{\gRegisteredLockUnlock}{{[}G11{]} The Registered User shall open/close a reserved car via app when he/she is close to it.}
\newcommand{\gPassengerShare}{{[}G12{]} The Passenger shall be able to use a car in shared mode.}
\newcommand{\gHandymanRecharge}{{[}G13{]} The Handyman Operator shall know the location of the car that has to be charged.}
\newcommand{\gHandymanReportIssue}{{[}G14{]} The Handyman Operator shall report any problem with a car.}

\begin{itemize}
	\item \gSystemDiscounts
	\item \gSystemFees
	\item \gSystemDistribution
	\item \gSystemShare
	\item \gVisitorSignUp
	\item \gRegisteredLogin
	\item \gRegisteredReserve
	\item \gRegisteredDeleteReservation
	\item \gRegisteredSearchDistance
	\item \gRegisteredSearchAddress
	\item \gRegisteredLockUnlock
	\item \gPassengerShare	
	\item \gHandymanRecharge
	\item \gHandymanReportIssue
\end{itemize}