\subsubsection{Scenario 1}
Chiara is an university student and a registered user to the service. Every day she uses public transportation to reach the school in the center of Milan. During the year because of the public transportation's strikes she is forced to find an alternative way to arrive at her destination.
Just the other week when she had to go to college for an exam, when she arrives to Cadorna station because of the metro service strike, decided to use the app \pej installed on her smartphone.
After checking that there is a car available in the equipped parking nearest her, she book it and went to the equipped parking to get to her destination. The car chosen is fully charged.
After using it for the most of the day Chiara brings back the car to the Cadorna's equipped parking. Once she parked, the system detects the end of the race and automatically computes the fare and applies a discount on this ride of 20\% because the battery car charge is more than 50\%. 
The transaction is performed automatically by the user's method of payment already chosen
\subsubsection{Scenario 2}
Antonio wants to spend the night at the club. He is registered to the car sharing service. He book a car by calling the call center. He gets the car at the equipped parking close to home by opening it with his smartphone, he goes to take Sofia and Elena. After a fun evening the group recovers the car to the disco's parking and return home. After bringing home all, Antonio brings the car to the initial equipped parking. Once he parked, the system detects the end of the race and automatically computes the fare and applies a discount on this ride of 10\% because for more than 50\% of the movement time, Antonio led at least two other passengers with him. The transaction is performed automatically by Antonio's method of payment already chosen
\subsubsection{Scenario 3}
Four friends live near Lambrate's station. They want to go to the San Siro stadium for a concert. Andrea is registered to the car sharing service. After checking that there is a car in Lambrate's station he goes to catch it. The group spent 30 minutes to arrive at the stadium. After the concert only Alessandro come back with Andrea. They spent 45 minutes because of an accident. At the end of the ride the system automatically computes the fare and doesn't apply a discount on this ride of 10\% because for more than 50\% of the movement time, there are only Andrea and Alessandro. The transaction is performed automatically by Andrea's method of payment already chosen
\subsection{Scenario 4}
Two group have to go from the Centrale's station to the Garibaldi's Station (both are equipped parking).
Adrian, Sonia and Alessandro are in the first group instead Claudio and Silvia are in the second group. Adrian and Claudio are registered to the service. Adrian reserves a car for a shared ride. Claudio looks for a shared ride and finds Adrian's ride and reserves the remaining two seats. When they arrive to Garibaldi's Station the ride is over and the system automatically computes the fare and applies a discount on this ride of 10\% because for more than 50\% of the movement time, the car was sold out.
The fare is shared between Adrian and Claudio (Adrian: 3/5 of the total amount, Claudio: 2/5 of the total amount). The transaction is performed automatically by the users' method of payment already chosen
\subsubsection{Scenario 5}
Alessia leaves the car at the Bovisa's equipped parking, despite the fact that the car needs to be recharged, she has no time to connect the car to the charging system. \\
Daniele, an handyman operator, using the \pej application is checking if there are cars that need to be recharged. The car number 5 needs to be connect. Daniele reach the car and connect it.
\subsubsection{Scenario 6}
Roberta, Maria and Luigi that have token their \pej's cars in other equipped parking leave them in the equipped parking A. The system realizes that there are too much cars in the equipped parking A and sends a message to  the handyman operator Fabio. The message says: "Move car 5 from the equipped parking A to the equipped parking B". Fabio moves the car to the indicated location.